Graph Generators for Data Science: A Survey

### 2018-06-08 generators_SocialNetworks.tex
Removed LFR from social networks

\paragraph{LFR} Lancichinetti, Fortnato and Radicchi (hence LFR)~\cite{PhysRevE.78.046110} develop a class of benchmark graphs whose nodes participate in internal community structures. The benchmark models directed and weighted real-world networks (e.g., social networks) containing overlapping communities of different sizes. The algorithm assumes that both the degree and the community size distributions are power laws. Each node shares a fraction $(1 - \mu)$ of its links with the other nodes of its community and a fraction $\mu$ with the other nodes of the network, where $\mu$ is called \emph{mixing parameter}. The sizes of the communities are taken from a power law distribution such that the sum of all sizes equals the number of nodes of the graph. The generation process starts with an empty graph and incrementally fills in the adjacency matrix by obeying the described constraints.

>>>>

%\paragraph{LFR} Lancichinetti, Fortnato and Radicchi (hence
%LFR)~\cite{PhysRevE.78.046110} develop a class of benchmark graphs whose nodes
%participate in internal community structures. The benchmark models directed and
%weighted real-world networks (e.g., social networks) containing overlapping
%communities of different sizes. The algorithm assumes that both the degree and
%the community size distributions are power laws. Each node shares a fraction $(1
%- \mu)$ of its links with the other nodes of its community and a fraction $\mu$
%with the other nodes of the network, where $\mu$ is called \emph{mixing
%parameter}. The sizes of the communities are taken from a power law distribution
%such that the sum of all sizes equals the number of nodes of the graph. The
%generation process starts with an empty graph and incrementally fills in the
%adjacency matrix by obeying the described constraints.
